Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-07 talk/dls2012/paper.tex
try to make this point a bit clearer

Loop peeling is achieved by appending an copy of the traced iteration at
the end of itself. See Figure~\ref{fig:overview} for an illustration.
The first part (called \emph{preamble}) finishes with a jump to the second part
(called the \emph{peeled loop}). The second part finishes with a jump to itself. This way
the preamble will be executed only once while the peeled loop will
be used for every further iteration. New variable names have to be
introduced in the entire copied trace in order to maintain the SSA-property.
Note that the peeled loop is not necessary the \emph{first} iteration of the
loop execution, it is general enough to correspond to any iteration of the loop.
However, the peeled loop can then be optimized using the assumption that a
previous iteration has happened.

>>>>

Loop peeling is achieved by appending an copy of the traced iteration at
the end of itself. See Figure~\ref{fig:overview} for an illustration.
The first part (called \emph{preamble}) finishes with a jump to the second part
(called the \emph{peeled loop}). The second part finishes with a jump to itself. This way
the preamble will be executed only once while the peeled loop will
be used for every further iteration. New variable names have to be
introduced in the entire copied trace in order to maintain the SSA-property.

When peeling the loop, no assumptions are made that the preamble is
the \emph{first} iteration when later executing the loop. The preamble stays
general enough to correspond to any iteration of the loop.
However, the peeled loop can then be optimized using the assumption that a
previous iteration (the preamble) has been executed already.
